\LaTeX{} 笔记模板

### 2023-04-02 note-temp/main-en.tex
update

\usepackage[numbers,sort&compress]{natbib}
\def\bibfont{\small}      % 修改参考文献字体
\setlength{\bibsep}{8pt}  % 调整参考文献间距
%\usepackage{subfig}

% --- 算法宏包及设置 ---
\usepackage{algorithm}
\usepackage{algpseudocode}
\floatname{algorithm}{Algorithm}
\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}

% --- 代码高亮 ---
%\input{matlab-style.tex}

@@

% --- 自定义命令 -----
\newcommand{\CC}{\ensuremath{\mathbb{C}}}
\newcommand{\RR}{\ensuremath{\mathbb{R}}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\ii}{\bm{\mathrm{i}}\,}  % 虚部
\newcommand{\bA}{\boldsymbol{A}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\mT}{\mathrm{T}}
\newcommand{\md}{\mathrm{d}}

%\title{\LaTeX 笔记模板}
%\author{某某某}
%\institute{}
%\version{1.3}
%\date{\zhtoday}
%\date{}

@@

\pagenumbering{Roman} % 页码为大写罗马数字

@@

% ----- generate a empty page -----
%\clearpage%
%\thispagestyle{empty}%
%\addtocounter{page}{-1}%
%\null%
%\clearpage

\clearpage
%\phantomsection
\pdfbookmark[1]{Contents}{toc}
\tableofcontents
\clearpage
\setlist[itemize]{label=$\circ$}

\pagenumbering{arabic}  % 页码为阿拉伯数字

%==========================================%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 正文内容从这里开始  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%% 参考文献 %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\phantomsection
\addcontentsline{toc}{section}{References} % 添加  "参考文献 " 到目录

% 生成参考文献, 使用第一种请把第二种全部注释

% 第一种方式, 使用 bib 文件

%\nocite{*}  % 可以暂时显示全部参考文献, 包括未引用的

\bibliography{reference}

% 第二种方式, 按照格式直接写文献信息, 使用第二种请把第一种全部注释

%\begin{thebibliography}{99}
%\bibitem{Tadmor2012} Tadmor~E. A review of numerical methods for nonlinear partial differential
%  equations\allowbreak[J]. Bull. Amer. Math. Soc., 2012, 49(4): 507-554.
%
%\bibitem{LiLiu1997} 李荣华, 刘播. 微分方程数值解法\allowbreak[M]. 东南大学出版社, 1997.
%
%\bibitem{Adams2003} Adams~R~A, Fournier~J~J~F. Sobolev spaces\allowbreak[M]. Elsevier, 2003.
%
%\bibitem{TreWei2014}Trefethen~L~N, Weideman~J~A~C. The exponentially convergent trapezoidal rule\allowbreak[J]. SIAM Rev., 2014, 56(3): 385-458.
%
%\bibitem{Shen1994} Shen~J. Efficient spectral-Galerkin method I. Direct solvers of second- and fourth-order equations using Legendre polynomials\allowbreak[J]. SIAM J. Sci. Comput., 1994, 15(6): 1489-1505.
%
%\end{thebibliography}

>>>>

\usepackage[numbers,sort&compress]{natbib}
%\def\bibfont{\small}      % bib font size
%\setlength{\bibsep}{8pt}  % vertical space of bib

%----- package for algorithm -----
\usepackage{algorithm}
\usepackage{algpseudocode}
\floatname{algorithm}{Algorithm}
\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}

%----- code highlight -----
%\lstset{basicstyle=\footnotesize\fontspec{Consolas}}
%\lstset{basicstyle=\footnotesize\fontspec{Courier New}}
%\newcommand*\lstinputpath[1]{\lstset{inputpath=#1}}
%\lstinputpath{{./M-files/}}

@@

%----- define new command -----
\newcommand{\CC}{\ensuremath{\mathbb{C}}}
\newcommand{\RR}{\ensuremath{\mathbb{R}}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\ii}{\bm{\mathrm{i}}\,}  % 虚部
\newcommand{\bA}{\boldsymbol{A}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\mT}{\mathrm{T}}
\newcommand{\md}{\mathrm{d}}

%\title{\LaTeX note template}
%\author{Author}
%\institute{}
%\version{1.3}
%\date{\zhtoday}
%\date{}

@@

@@

%----- generate a empty page -----
%\clearpage%
%\thispagestyle{empty}%
%\addtocounter{page}{-1}%
%\null%
%\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{Roman} % page is Roman numerals

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
%\phantomsection
\pdfbookmark[1]{Contents}{toc}
\tableofcontents
\clearpage

\setlist[itemize]{label=$\circ$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{arabic}  % page is arabic numerals

%%%%%%%%%%%%%%%%%%%%%% Body Here %%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{code highlight}

MATLAB code

\begin{lstlisting}[style=matlab,title={MATLAB code}]
% Euler method for the ODE model
% u'(x)=x^2+x-u, x in [0,1]
% Initial condition: u(0)=0 ;
% Exact solution: u(x)=-exp(-x)+x^2-x+1.
clear all;  clf
h=0.1;
x=0:h:1;
N=length(x)-1;
u(1)=0;                        % initial value
fun=@(t,u) t.^2+t-u;           % RHS

for n=1:N
    u(n+1)=u(n)+h.*fun(x(n),u(n));
end

ue=-exp(-x)+x.^2-x+1;          % exact solution
plot(x,ue,'b-',x,u,'r+','LineWidth',1)
legend('Exact','Numerical','location','North')
%title('Euler method','fontsize',12)
set(gca,'fontsize',12)
xlabel('x','fontsize',16), ylabel('u','fontsize',16,'Rotation',0)
\end{lstlisting}

Python code

\begin{lstlisting}[style=python,title={Python code}]
#PythonDraw.py
import turtle as t
t.setup(650, 350, 200, 200)
t.penup()
t.fd(-250)
t.pendown()
t.pensize(25)
t.pencolor("purple color")
t.seth(-40)
for i in range(4):
    t.circle(40, 80)
    t.circle(-40, 80)
t.circle(40, 80/2)
t.fd(40)
t.circle(16, 180)
t.fd(40 * 2/3)
t.done()
\end{lstlisting}

%%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\phantomsection
\addcontentsline{toc}{section}{References}

%\nocite{*}
\bibliography{reference}

%\begin{thebibliography}{99}
%\bibitem{Adams2003} Adams~R~A, Fournier~J~J~F. Sobolev spaces[M]. Elsevier, 2003.
%
%\bibitem{GoVa2013} Gene~H. Golub and Charles~F. Van~Loan. Matrix computations. The Johns Hopkins University Press, Baltimore, 4th edition, 2013.
%
%\bibitem{Shen1994} Shen~J. Efficient spectral-Galerkin method I. Direct solvers of second- and fourth-order equations using Legendre polynomials[J]. SIAM J. Sci. Comput., 1994, 15(6): 1489-1505.
%
%\bibitem{Tadmor2012} Tadmor~E. A review of numerical methods for nonlinear partial differential
%  equations[J]. Bull. Amer. Math. Soc., 2012, 49(4): 507-554.
%
%\bibitem{TreWei2014} Trefethen~L~N, Weideman~J~A~C. The exponentially convergent trapezoidal rule[J]. SIAM Rev., 2014, 56(3): 385-458.
%
%\end{thebibliography}
